
---
title: "Error Correction"
author: "Yang Xing yx2416 and Hongru Liu hl3148"
date: "11/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 0. Load libraries, source customized functions, load needed output files

```{r}
# Please change the working directory to the folder containing this Rmd file.
setwd("/Users/hongru/Documents/GitHub/Fall2018-Project4-sec1proj4_grp6/Github/doc/")

if(!require("tm")){
  install.packages("tm")
}
if(!require("purrr")){
  install.packages("purrr")
}
if(!require("stringr")){
  install.packages("stringr")
}
library(tm)
library(purrr)
library(stringr)

source("../lib/get_text.R")
source("../lib/correction_function.R")

load("../output/ground_truth_words_cleaned.Rdata")
load("../output/ground_truth_onelines.Rdata")
load("../output/ground_truth_table.Rdata")
load("../output/tesseract_labels.Rdata")
load("../output/tesseract_words_cleaned.Rdata")
```

## 1. Import Confusion Matrix

```{r}
sub <- read.csv("../data/sub_matrix.csv")
rownames(sub)<-sub[,1]
sub<-sub[,-1]
rev <- read.csv("../data/rev_matrix.csv")
rownames(rev)<-rev[,1]
rev<-rev[,-1]
del <- read.csv("../data/del_matrix.csv")
rownames(del)<-del[,1]
del<-del[,-1]
add <- read.csv("../data/add_matrix.csv")
rownames(add)<-add[,1]
add<-add[,-1]
```

## 2.Example of correction function

```{r}
strip.text("$Don't#0125adb")
Transpositions("yes")
Deletes("yes")
Insertions("yes")
Replaces("yes")
Neighbors('yes')
  length(Neighbors('yes'))
Neighbors_clean('yes',ground_truth_table)
Clean(Insertions("yes"))
Probability_MLE("great",ground_truth_words_cleaned)
Probability_ELE("great",ground_truth_words_cleaned)
coun("great",ground_truth_words_cleaned)
```

## 3. Count the frequency of each letter (a-z) in the ground truth

```{r}
#letter_count <- lapply(letters,coun,ground_truth_words_cleaned)
#names(letter_count) <- letters
load("../output/letter_count.Rdata")
```

## 4. Count the frequency of different combine of letters

```{r}
# combine <- rep(0,676)
# dim(combine) <- c(26,26)
# combine <- data.frame(combine)
# rownames(combine) <- letters
# colnames(combine) <- letters
# combine_count <- combine
# for (i in letters){
#   for(j in letters){
#    combine[i,j]<- paste0(i,j)
#    combine_count[i,j]<-coun(combine[i,j],ground_truth_words_cleaned)
#   }
# }
load("../output/combine_count.Rdata")
```

## 5 Error correction

### 5.1 Example of functions
```{r}
p_tc_sub("access")
p_tc_ins("acess")
p_tc_del("acress")
p_tc_tran("acess")
candidates("yaung")
Correct("yaung")
```

### 5.2 Find correction candidates using both MLE and ELE without Context

```{r}
errors <- list()
for (i in 1:length(tesseract_labels)) {
  errors[[i]] <- names(tesseract_labels[[i]])[tesseract_labels[[i]]==1]
}
errors <- unlist(unlist(errors))

# corrected_ts <- lapply(errors, Correct, ground_truth_words_cleaned)
load("../output/corrected_ts.Rdata")

corrected_ts_MLE <- names(unlist(lapply(lapply(corrected_ts,"[[",1),"[",1)))
corrected_ts_ELE <- names(unlist(lapply(lapply(corrected_ts,"[[",2),"[",1)))
all_detected_errors <- errors
corrected_words_MLE <- corrected_ts_MLE[nchar(corrected_ts_MLE)!=0]
not_corrected_MLE <- errors[nchar(corrected_ts_MLE)==0]
corrected_words_ELE <- corrected_ts_ELE[nchar(corrected_ts_ELE)!=0]
not_corrected_ELE <- errors[nchar(corrected_ts_ELE)==0]
sapply(list(corrected_MLE=corrected_words_MLE,
            not_corrected_MLE=not_corrected_MLE,
            corrected_ELE=corrected_words_ELE,
            not_corrected_ELE=not_corrected_ELE),head,10)
```

### 5.3 Error Correction using both MLE and ELE with Context

```{r}
error_label<-unlist(unlist(tesseract_labels))
t<-unlist(unlist(tesseract_words_cleaned))
g<-paste0(unlist(unlist(ground_truth_words_cleaned)),collapse = " ")

Left<-0
Left<-append(Left,t[which(error_label==TRUE)-1])
names(Left)<-errors
Right<-t[which(error_label==TRUE)+1]
names(Right)<-errors

# corrected_context <- lapply(1:50916,Correct_c4)
load("../output/corrected_context.Rdata")

corrected_context_candi_MLE <- lapply(corrected_context,"[[",2)
corrected_context_candi_ELE <- lapply(corrected_context,"[[",3)
corrected_context_word_MLE <- unlist(lapply(corrected_context_candi_MLE,names)[!sapply(corrected_context_candi_MLE,is.null)])
not_corrected_context_MLE <- errors[sapply(corrected_context,is.null)]
corrected_context_word_ELE <- unlist(lapply(corrected_context_candi_ELE,names)[!sapply(corrected_context_candi_ELE,is.null)])
not_corrected_context_ELE <- errors[sapply(corrected_context,is.null)]
### View the corrrection results
sapply(list(corrected_MLE=corrected_context_word_MLE,
            not_corrected_MLE=not_corrected_context_MLE,
            corrected_ELE=corrected_context_word_ELE,
            not_corrected_ELE=not_corrected_context_ELE),head,10)
```

### 6. Save all needed results
```{r}
save(letter_count,file="../output/letter_count.Rdata")
save(combine_count,file="../output/combine_count.Rdata")
save(corrected_ts,file="../output/corrected_ts.Rdata")
save(corrected_context,file="../output/corrected_context.Rdata")
save(all_detected_errors,corrected_words_MLE,not_corrected_MLE,corrected_words_ELE,not_corrected_ELE,file="../output/correction_results_without_context.Rdata")
save(all_detected_errors,corrected_context_word_MLE,not_corrected_context_MLE,corrected_context_word_ELE,not_corrected_context_ELE,file="../output/correction_results_with_context.Rdata")
```







