---
title: "Project 4 - Error Detection"
author: "Hongru Liu hl3148"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---

## Step 0: environment setting

### Load libraries, source customized functions

```{r}
# Please change the working directory to the folder containing this Rmd file.
setwd("/Users/hongru/Documents/GitHub/Fall2018-Project4-sec1proj4_grp6/Github/doc")

if(!require("tm")){
  install.packages("tm")
}
if(!require("qdap")){
  install.packages("qdap")
}
if(!require("purrr")){
  install.packages("purrr")
}
library(tm) # VCorpus
library(qdap) # clean
library(purrr)

source("../lib/get_text.R")
source("../lib/bigramize.R")
source("../lib/make_label.R")
```

## Step 1: construct a positional binary matrix using ground truth texts

### 1.1 Read the ground truth text from files.

```{r}
ground_truth_dir <-"../data/ground_truth"
ground_truth_file_name <- list.files(ground_truth_dir)
ground_truth_file_path <- paste0(ground_truth_dir,'/',ground_truth_file_name)
ground_truth_onelines <- lapply(ground_truth_file_path,get_text)
```

### 1.2 Clean the ground truth texts, convert them to words and sort the words by letter length.

*Clean the text by removing all numbers, punctuations, special symbols. Only letters are retained*

```{r}
ground_truth_words_cleaned <- unlist(lapply(ground_truth_onelines,clean_text))
ground_truth_by_length <- sort_by_length(ground_truth_words_cleaned)
ground_truth_table <- table(ground_truth_words_cleaned)
### View 10 words of ground trurh dictionary
tail(head(ground_truth_table,100),10)
```

### 1.3 Construct letter bigrams for the ground truth words

*Note that for the final result, we construct a positional binary list of letter bigrams instead of a matrix. But the former one could be used in the same way as the latter one.*

```{r}
### Construct letter bigrams for the words having length >= 3
num_len <- length(ground_truth_by_length)
ground_truth_bigram_from3 <- lapply(ground_truth_by_length[3:num_len],bigramize)
### include words having length <= 2
ground_truth_bigram <- c(list(l_1=list(PD_1=ground_truth_by_length[[1]]),
                              l_2=list(PD_1_2=ground_truth_by_length[[2]])),
                         ground_truth_bigram_from3)
### romove duplicate bigrams
ground_truth_unibig <- lapply(ground_truth_bigram,unique_bigram) ### this is the final bigram list for error detection
### View the bigram matrix of 4-letter length words of ground truth
lapply(ground_truth_unibig[[4]],head)
### calculate the number of bigrams
sum(unlist((lapply(ground_truth_unibig,function(x) {lapply(x,length)}))))
```

## Step 2: construct a word list using tesseract texts

### 2.1 Read the tesseract text from files.

```{r}
tesseract_dir <- "../data/tesseract"
tesseract_file_name <- list.files(tesseract_dir)
tesseract_file_path <- paste0(tesseract_dir,'/',tesseract_file_name)
tesseract_onelines <- lapply(tesseract_file_path,get_text)
```

### 2.2 Clean the tesseract texts, convert them to words.

```{r}
tesseract_words_cleaned <- lapply(tesseract_onelines,clean_text)
### View the first six words of first five tesseract files
lapply(tesseract_words_cleaned[1:5],head)
```

## Step 3: error detection

### 3.1 Construct a label list that indicates whether a word in the given string is an error. 

`label = 1` means the corresponding word is an error and `label = 0` means the word is not an error

```{r}
tesseract_labels <- make_label(tesseract_words_cleaned,ground_truth_unibig)
### change names of label lists
names(tesseract_labels) <- ground_truth_file_name
for (i in 1:length(tesseract_labels)) {
  names(tesseract_labels[[i]]) <- unlist(strsplit(tesseract_words_cleaned[[i]]," "))
}
### View the first 10 words' labels of first five tesseract files
lapply(tesseract_labels[1:5],head)
```

### 3.2 Preliminary result analysis

```{r}
error_rate <- (sapply(tesseract_labels, sum)/sapply(tesseract_words_cleaned, length))
summary(error_rate)
```

## Step 4: save needed results

```{r}
save(ground_truth_onelines,file="../output/ground_truth_onelines.Rdata")
save(ground_truth_words_cleaned,file="../output/ground_truth_words_cleaned.Rdata")
save(ground_truth_table,file="../output/ground_truth_table.Rdata")
save(ground_truth_unibig,file="../output/ground_truth_unibig.Rdata")
save(tesseract_words_cleaned,file="../output/tesseract_words_cleaned.Rdata")
save(tesseract_labels,file="../output/tesseract_labels.Rdata")
```

